Labelling Plot Panels

### 2013-10-22 _knitr-posts/2013-10-21-panel-letters.Rmd
Update panel letters and plyr posts

> I've got a multipanel plot and simply want to add "(a)", "(b)", etc. to it.
> I've always cheated and used legend:
>
> ```
> add.label <- function(label, ...) legend("topleft", legend=" ", title=label,
> bty='n', ...)
> ```
>
> which works great for a topleft position. But for bottomright it isn't
> right. I can adapt it to:
>
> ```
> add.label2 <- function(label, position="topleft", ...) legend(x=position,
> legend=label, bty='n', ...)
> ```
>
> and that works great, but then doesn't work for topleft!
>
> There has got to be a non-hack way to do this simple (and common) task.

I'd never thought of using `legend()` for that purpose, but that's a neat
hack.

@@

And we can use `text()` combined with `par("usr")` to align these labels.
`par("usr")` gives us the coordinates of the plotting region in the order `x1,
x2, y1, y2`. Therefore, we can do the following to place the labels 2% over
from the left and 7% down from the top:

>>>>

> I've got a multipanel plot and simply want to add "(a)", "(b)", etc. to it.
> I've always cheated and used legend:
>
> ```
> add.label <- function(label, ...) legend("topleft", legend=" ", title=label,
> bty='n', ...)
> ```
>
> which works great for a topleft position. But for bottomright it isn't
> right. I can adapt, and that works great, but then it doesn't
> work for topleft!
>
> There has got to be a non-hack way to do this simple (and common) task.

I'd never thought of using `legend()` for that purpose, but that's a neat
hack. If you wanted to stick with `legend()`, you could just
pass the position to the function:

```{r panel_letters5, fig.width=6, fig.height=3}
add_label_legend <- function(pos = "topleft", label, ...) {
  legend(pos, label, bty = "n", ...)
}

par(mfrow = c(1, 2), mar = c(2, 2.5, 0, 0))
for(i in 1:2) {
  plot(1)
  add_label_legend("topleft", paste0("(", letters[i], ")"))
  add_label_legend("topright", paste0("(", letters[i], ")"))
  add_label_legend("bottomright", paste0("(", letters[i],
      ")"))
  add_label_legend("bottomleft", paste0("(", letters[i], ")"))
}
```

But, you don't get a lot of control over precisely how the
label is positioned.

@@

You can use `text()` combined with `par("usr")` to align these labels.
`par("usr")` gives us the coordinates of the plotting region in the order `x1,
x2, y1, y2`. Therefore, we can do the following to place the labels 2% over
from the left and 7% down from the top:
